---
title: "Data Product Assignment"
author: "Mahmoud Samy"
date: "January 3, 2019"
output:
  slidy_presentation: default
  beamer_presentation: default
  ioslides_presentation: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
##Statistical Analysis of mtcars Dataset

-My Goal is  Create a Web Page Presentation using R Markdown that features a plot created with Plotly.and then Hosting my webpage on either GitHub Pages, RPubs, or NeoCities. 

-For Example i will use mtcars Dataset to undestand the Relationship of MPG to other Factors
 and Show my Data Visualization.

## Understanding Gas Mileage(MPG)

We plot `wt` vs.`mpg` and visualize the number of `cyl` as colors
and the amount of `hp` as the size of an individual point in the plot.


## Visualizing the Data

```{r plot,fig.cap='My Figure',fig.align='center'}
suppressPackageStartupMessages(library(plotly))
plot_ly(data = mtcars, x = ~wt, y = ~mpg, 
        color = ~as.factor(cyl), size = ~hp,
        text = ~paste("Weight: ", wt, '<br>MPG:', mpg),
        type = "scatter", mode = "markers") %>%
  layout(title = "Car Data")
```

